Issues with Dynamical Measurements Across the Disk

### 2019-02-15 paper/ms.tex
Add text introducing Fig 4

\begin{figure}
\plotone{fig/schmactions_Jz_hist.pdf}
\caption{A histogram of the observed values in $J_z$ for the thick orbit
assuming a $z$ offset of $100\,\pc$. One can see that if the observed $z$
values have a bias (from e.g. an incorrectly computed midplane), then the
induced error distribution in $J_z$ is decidedly non-Gaussian. Therefore, any
sort of error propagation must take this into account.}
\label{fig:Jz_hist}
\end{figure}

>>>>

\begin{figure}
\plotone{fig/schmactions_Jz_hist.pdf}
\caption{A histogram of the observed values in $J_z$ for the thick-disk orbit
assuming a $z$ offset of $100\,\pc$. One can see that if the observed $z$
values have a bias (from e.g. an incorrectly computed midplane), then the
induced error distribution in $J_z$ is decidedly non-Gaussian. Therefore, any
sort of error propagation must take this into account.}
\label{fig:Jz_hist}
\end{figure}

In Figure~\ref{fig:Jz_hist} we plot a histogram of the observed values of
$J_z$ for the thick-disk orbit assuming a $z$ offset of $100\,\pc$ (i.e. the
{\em right} panel of Figure~\ref{fig:one_orbit_wrong_ref}). The true value of
$J_z$ is plotted as a vertical dashed line. Here we see that the spread in
$J_z$ induced by a systematic offset in $z$ is non-Gaussian and bimodal.
Furthermore, neither of the modes lie at the true value of $J_z$.
